The 2024 U.S. Presidential Election Forecast

### 2024-11-02 other/literature/ElectionForcast_linearmodel.qmd
literature grammar fixed

The purpose of this document is to explain the details used in the linear model.This linear model is used to forecast the U.S. 2024 president election by predicting the wining rate outcomes of polls based on several features of polls. Broadly, the model can be described as a Linear hierachical model:

@@

2.Each independent variables in this model is consider distributed normally, so as the intercept.

@@

For numeric variables, we chose either the mean or the median as the representative feature value, depending on the data's distribution.
If the data distribution was approximately symmetric (low skewness), we used the mean, as it best represents the central tendency。

For highly skewed data, we used the median to avoid the influence of outliers, providing a more robust measure of central tendency.

@@

### Load Models and Data
The linear models for both Trump and Harris were loaded using readRDS(). We use ths featured value mentioned before as input values in our model.

>>>>

The purpose of this document is to explain the details used in the linear model. This linear model is used to forecast the U.S. 2024 president election by predicting the wining rate outcomes of polls based on several features of polls. Broadly, the model can be described as a linear hierarchical model:

@@

2. Each independent variable in this model is consider distributed normally, so as the intercept.

@@

For numeric variables, we chose either the mean or the median as the representative feature value, depending on the data distribution.
If the data distribution was approximately symmetric (low skewness), we used the mean, as it best represents the central tendency。

For highly skewed data, we used the median to avoid the influence of the outliers, providing a more robust measure of central tendency.

@@

### Load Models and Data
The linear models for both Trump and Harris were loaded using readRDS(). We use this featured value mentioned before as input values in our model.
